Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-21

### 2016-02-23 ec-2016/source/paper.tex
Add to section: multipath fault tolerance.

They key idea behind multipath fault tolerance is that several copies of
a message are sent, along multiple routes,
rather than using traditional unicast routing.
If any of the message copies differ from one another or do not arrive,
the receiver can conclude that an error has occurred,
and possibly correct it, depending on the magnitude of the error
and the desired fault tolerance properties.
In the simplest such scheme, a sender broadcasts copies of a message
along all possible routes to the receiver.
Such an approach takes advantage of all possible redundancy in the network,
and requires an adversary to compromise at least one node on each path
in order to create an undetectable error.
Realistically, the sender may only have the resources to send a limited number of
copies, or the network may not be able to handle the congestion caused by
sending all messages along all paths.
However, we will now show that a network can provide a high level of
fault tolerance with only a few copies of a message,
provided the number of possible paths is large.

>>>>

They key idea behind multipath fault tolerance is that several copies of
a message are sent, along multiple routes,
rather than using traditional unicast routing.
If any of the message copies differ from one another or do not arrive,
the receiver can conclude that an error has occurred,
and possibly correct it, depending on the magnitude of the error
and the desired fault tolerance properties.

In the simplest such scheme, a sender (Alice) broadcasts copies of a message
along all possible routes to the receiver (Bob).
Such an approach takes advantage of all possible redundancy in the network,
and requires an adversary (Eve) to compromise at least one node on each path
in order to create an undetectable error.
But how many nodes is that?
The answer depends on the smallest {\em vertex cut} of the untrusted
portion of the network---the smallest set of nodes than can be removed
to separate the network into two components.
Any path between Alice and Bob must pass through all such sets,
so to guarantee an undetectable error, Eve must compromise at least as many
nodes as are in the smallest vertex cut.
Alice and Bob's trust boundaries are both vertex cuts,
so the smaller of the two is an upper bound.
It is not difficult to construct networks in which the trust boundary is exactly
the smallest vertex cut,
and we will show this to be true for the networks we consider below.
We denote the size of the smallest vertex cut---the
maximum number of disjoint paths between Alice and Bob's trusted
neighborhoods---as $B$.

Realistically, the sender may only have the resources to send a limited number of
copies, or the network may not be able to handle the congestion caused by
sending all messages along all paths.
However, we will now show that a network can provide a high level of
fault tolerance with only a few copies of a message,
provided the number of disjoint paths $B$ is large.

In a more sophisticated multipath fault tolerance scheme,
Alice randomly chooses $k$ paths and sends a copy of
her message on each.
We further assume that Alice posesses a routing algorithm
(such as described in the next section)
that enables her to construct paths that
do not intersect between trusted neighborhoods.
So the maximum number of paths Alice could choose is $B$,
otherwise two paths would have to intersect in the minimum vertex cut.
Let us assume that Eve is capable of compromising up to $l$ nodes.
Eve's best adversarial strategy is now to compromise as many nodes in the smallest
vertex cut as possible,
succeeding when each of Alice's paths include one of the compromised nodes.
Since Alice chooses paths randomly,
all nodes in the vertex cut are equally likely to contain a path,
so Eve can do no better than also choosing randomly.
If $k > l$, at least one message will get through uncompromised and all
errors are detectable.
Otherwise, the probability of Eve producing an undetectable error is
the probability that all of Alice's paths contain compromised nodes:
\beq
TODO
\eeq
